An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-23 neurips-19/poly-embed.tex
Addressed Bo's comment in sec 2.3
notes to jessie on top-k

Note that it is not clear if embeddings give rise to calibrated links; indeed, apart from mapping the embedded points back to their original reports via $\psi(\varphi(r)) = r$, how to map the remaining values is far from clear.
We address the question of when embeddings lead to calibrated links in Section~\ref{sec:poly-loss-embed}.
\bo{I think in Section \ref{sec:calibration} ?}

@@

>>>>

Note that it is not clear if embeddings give rise to calibrated links; indeed, apart from mapping the embedded points back to their original reports via $\psi(\varphi(r)) = r$, how to map the remaining values is far from clear.
We address the question of when embeddings lead to calibrated links in Section~\ref{sec:calibration}.
%\bo{I think in Section \ref{sec:calibration} ?}

@@

\raf{Jessie: stuff to update / change:}
  \begin{itemize}
  \item Need to mention the link function typically used; don't see it anywhere
  \item You keep saying $L(r,y)$ not $L(r)_y$ for all losses
  \item Let's use our property notation; $\prop{L_2}$ instead of argmins
  \item The story we discussed: YK show $L_2$ is inconsistent.  Our framework lets us ask: with what discrete loss \emph{is} $L_2$ consistent?  (It also assures us that $L_2$ is consistent for something...)
  \item The next part of the story: oh look, $L_2$ embeds something which is $\ell_{top-k}$ plus some other term, so (a) we can see very clearly what $L_2$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.
  \item Domain of $\ell_2$ should not be $\{0,1\}^n$ anymore
  \end{itemize}
